Verifying Demonstrations

### 2018-11-06 paper/privacy-properties.tex
Fixes typo

Thus, in our context the crucial property is therefore privacy.
More precisely for the protester, we want unlinkability between a protester's real identity \(P\) and the cause identifier \(\cid\) against the adversary.
Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice's due to some auxiliary knowledge, she should not be able to link it to another proof (\eg, from a different protest).

>>>>

Thus, in our context the crucial property is therefore privacy.
More precisely for the protester, we want unlinkability between a protester's real identity \(P\) and the cause identifier \(\cid\) against the adversary.
Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
Furthermore, if Grace has managed to link one proof to Alice due to some 
auxiliary knowledge, she should not be able to link it to another proof (\eg, 
from a different protest).
